%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[]{awesome-cv}
\usepackage{textcomp}
\hypersetup{%
  colorlinks=true,% hyperlinks will be coloured
  linkbordercolor=blue,% hyperlink border will be red
}
%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{resume/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]
\renewcommand*{\cventry}[5]{%
  \vspace{-2.0mm}
  \setlength\tabcolsep{0pt}
  \setlength{\extrarowheight}{0pt}
  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} L{\textwidth - 4.5cm} R{4.5cm}}
    \ifempty{#2#3}
      {\ifempty{#1#4}{}{\entrypositionstyle{#1} & \entrydatestyle{#4} \\}}
      {\entrytitlestyle{#2} & \entrylocationstyle{#3} 
       \ifempty{#1#4}{}{\\\entrypositionstyle{#1} & \entrydatestyle{#4}}}
    \ifempty{#5}{}{\\\multicolumn{2}{L{\textwidth}}{\descriptionstyle{#5}}}
  \end{tabular*}%
  \par % <============================================================== missing in class
}

\usepackage{atbegshi,picture}
\AtBeginShipout{\AtBeginShipoutUpperLeft{%
  \put(\dimexpr\paperwidth-1cm\relax,-1.5cm){\makebox[0pt][r]{\framebox{Every colored text is a link.}}}%
}}

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Profile
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
	\headerfirstnamestyle{\textbf{Ayrton}} \ \headerlastnamestyle{San Joaquin} \\
	\vspace{1mm}
	\headerpositionstyle{\faFlask \href{https://scholar.google.com/citations?user=e4UX388AAAAJ&hl=en}{Scientist, Trustworthy AI} | \faPencil \href{https://medium.com/@ajsanjoaquin}{Writer}} \\
	\vspace{1mm}
	{\faEnvelope\ ayrton@aya.yale.edu} | \iffalse {\faMobile\ +65 88147588} | \fi {\faMapMarker\ Barcelona, Spain} | \faGithub\ \href{https://github.com/ajsanjoaquin}{ajsanjoaquin} | {\faLinkedinSquare\ \href{https://www.linkedin.com/in/ajsanjoaquin/}{ajsanjoaquin}}| {\faLegal\ \href{http://ajsanjoaquin.github.io/values}{Values}}
\end{center}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\vspace{1mm}
\cvsection{Education}
\begin{cventries}
	\cventry
	{BSc. (Honors) in Data Science, Minor in Philosophy. \textbf{(Scholar, With High Distinction)}}
	{Yale-NUS College}
	{Singapore}
	{August 2018 - May 2023}
	{Semester Abroad at the University of Copenhagen, Denmark}
\end{cventries}
\vspace{-3mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Experience}
\begin{cventries}
	\cventry
	{Research Analyst}
	{AI Standards Lab}
	{Singapore \& Spain}
	{August 2024 - Present}
	{\begin{cvitems}
		\item Contributing to the Codes of Practice of the EU AI Act.
	\end{cvitems} }
	\vspace{-2mm}

	\cventry
	{AI Scientist, \href{https://descartes.cnrsatcreate.cnrs.fr/}{DesCartes program}}
	{French National Centre for Scientific Research (CNRS)@CREATE \newline International Research Laboratory on Artificial Intelligence (\href{https://ipal.cnrs.fr/}{IPAL}- by appointment) }
	{Singapore}
	{September 2023 - August 2024}
	{\begin{cvitems}
		\item {Led a Franco-Singaporean team studying efficient fine-tuning of Large Language Models (LLMs). Published at EMNLP Findings 2024.}
		\item {Created and curated the Tagalog dataset of \href{SeaEval}{https://seaeval.github.io/}, a multilingual benchmark for Southeast Asian Languages.}
	\end{cvitems}}
	\vspace{-2mm}
	\cventry
	{Scholar}
	{Machine Learning Safety Scholars Program, Center for AI Safety}
	{Palo Alto, United States}
	{June 2022 - August 2022}
	{\begin{cvitems}
		\item {Studied model failures (CV and NLP), and led research on analyzing LLMs using few-shot learning.}
		\item{Implemented various strategies in \textbf{robustness} (PGD, adversarial training), \textbf{anomaly detection} (AUROC, ViM), \textbf{calibration} (RSME, Brier scores), and \textbf{trojan attacks} (data poisoning).}
	\end{cvitems}}
	\vspace{-2mm}
	\cventry
	{Undergraduate Researcher}
	{Data Privacy and Trustworthy Machine Learning Lab, NUS}
	{Singapore}
	{May 2021 - March 2022}
	{\begin{cvitems}
		\item {Collaborated with Google DeepMind on privacy and adversarial machine learning research for my bachelor's thesis in a team across 4 time zones. \textbf{Published in a top security conference (ACM CCS) as the youngest and only undergraduate co-author.}}
	\end{cvitems}}
	\vspace{-2mm}
	\cventry
	{Deep Learning Engineer}
	{Arterys (Freelance)}
	{San Francisco, United States}
	{March 2020 - June 2020}
	{\begin{cvitems}
		\item {Created a COVID-19 Pneumonia classifier \textbf{4 days after pandemic declaration in collaboration with A.I. Singapore}.}
		\item {Collaborated with Arterys to \href{https://www.linkedin.com/feed/update/urn:li:activity:6676702441607716864/}{deploy the model in their platform} 
		for use by American hospitals and researchers. Model engineer in a team of 4 across 3 time zones.}
	\end{cvitems}}
\end{cventries}

\vspace{-5mm}
\cvsection{Honors \& Public Service}
\begin{cventries}
	\cventry
	{}
	{\href{https://www.aisafetyconnect.com/}{AI Safety Connect 2025}}
	{Paris, France}
	{}
	{• Invited to present about risk management, an official side-event of the Paris AI Action Summit.}
	\vspace{-1mm}

	\cventry
	{}
	{\href{https://www.iaseai.org/conference}{International Association for Safe and Ethical AI Conference 2025}}
	{Paris, France}
	{}
	{• Invited to present about risk management at IASEAI Conference, an official side-event of the Paris AI Action Summit}
	\vspace{-1mm}

	\cventry
	{}
	{\href{https://asiatechxsg.com/aisummitsingapore/speakers/ayrton-san-joaquin/}{The AI Summit Singapore 2024}}
	{Singapore}
	{}
	{• Invited as a featured speaker to dicuss about data privacy for Generative AI at Asia Tech x Singapore, co-hosted by the Singapore Government.}
	\vspace{-1mm}

	\cventry
	{}
	{\href{https://publicai.network/}{Public AI Advocacy}}
	{Global}
	{}
	{• Co-authored a foundational document of a global network of AI researchers, policymakers, and practitioners to center AI research and development in the public interest and as public infrastructure.}
	\vspace{-1mm}

	\cventry
	{}
	{\href{https://github.com/ajsanjoaquin/meta-aria}{Project Aria Timeline Builder Workshop 2023}}
	{Menlo Park, United States}
	{}
	{• Invited by Meta Reality Labs to design a use-case for \href{https://about.meta.com/en/realitylabs/projectaria/}{Project Aria}. Participated as the only bachelor's graduate among 20 graduate and postdoctoral researchers. \href{https://drive.google.com/file/d/1ymkkCU31EP57DDXJpdB9NIuVrsMtZB9t/view?usp=drive_link}{Video demo.}}
	\vspace{-1mm}
	
\end{cventries}

\vspace{-3mm}
\cvsection{Publications}
\vspace{-3mm}
\begin{cvhonors}
	\cvhonor
	{\textnormal{Gipiškis, R. and} San Joaquin, A., \textnormal{et. al.} }
	{Risk Sources and Risk Management Measures in Support of Standards for General-Purpose AI Systems. \textit{Under Review}}
	{\href{https://arxiv.org/pdf/2410.23472}{link}}
	{January 2025}
	\cvhonor
	{San Joaquin, A., \textnormal{et. al.} }
	{In2Core: Leveraging Influence Functions for Coreset Selection in Instruction Finetuning of Large Language Models. \textit{EMNLP Findings 2024} }
	{\href{https://arxiv.org/abs/2212.01933}{link}}
	{November 2024}
	\cvhonor
	{\textnormal{Tramer, F., \dots ,} San Joaquin, A., \textnormal{ et.al.} }
	{Truth Serum: Poisoning Machine Learning Models to Reveal Their Secrets. \textit{ACM Conference on Computer and Communications Security (CCS) 2022}}
	{\href{https://dl.acm.org/doi/10.1145/3548606.3560554}{link}}
	{November 2022}
\end{cvhonors}

\vspace{-6mm}
%\cvsection{Press}
%\vspace{-3mm}
%\begin{cvhonors}
%	\cvhonor
%	{\href{https://www.theregister.com/2022/04/12/machine_learning_poisoning}{Machine learning models leak personal info if training data is compromised}}
%	{\textit{The Register}}
%	{}
%	{April 2022}
%\end{cvhonors}

%\vspace{-3mm}

% \cvsection{Skills}
% \vspace{-3mm}
% \begin{cventries}
% 	\cventry
% 	{}
% 	{\def\arraystretch{1.15}{\begin{tabular}{ l l }
% 		Machine Learning:  & {\skill{ Pytorch, Sickit-Learn, JAX, HuggingFace, Langchain, NLTK, Spacy}} \\
% 		Data:  & {\skill{Pandas, PySpark, Querying (SQL, MySQL, MongoDB), Vector Database (Qdrant, Pinecone)}} \\
% 		MLOps: & {\skill{Linux, Git, GCP, AzureML, Snowflake, Docker, Flask, Continuous Integration, Kubernetes}} \\
% 	\end{tabular}}}
% 	{}
% 	{}
% 	{}
% \end{cventries}
\vspace{-20mm}
\end{document}